\begin{thebibliography}{10}
\bibitem{jelodar_latent_2019}
Hamed Jelodar, Yongli Wang, Chi Yuan, Xia Feng, Xiahui Jiang, Yanchao Li, and
  Liang Zhao.
\newblock Latent {Dirichlet} allocation ({LDA}) and topic modeling: models,
  applications, a survey.
\newblock {\em Multimedia Tools and Applications}, 78(11):15169--15211, June
  2019.

\bibitem{gupta_pan_lda_2021}
Aakansha Gupta and Rahul Katarya.
\newblock {PAN}-{LDA}: {A} latent {Dirichlet} allocation based novel feature
  extraction model for {COVID}-19 data using machine learning.
\newblock {\em Computers in Biology and Medicine}, 138:104920, November 2021.

\bibitem{pichardo_lagunas_svd_lda_2015}
Sergey Nikolenko.
\newblock {SVD}-{LDA}: {Topic} {Modeling} for {Full}-{Text} {Recommender}
  {Systems}.
\newblock In Obdulia Pichardo~Lagunas, Oscar Herrera~Alcántara, and Gustavo
  Arroyo~Figueroa, editors, {\em Advances in {Artificial} {Intelligence} and
  {Its} {Applications}}, volume 9414, pages 67--79. Springer International
  Publishing, Cham, 2015.
\newblock Series Title: Lecture Notes in Computer Science.

\bibitem{selvi_classification_2019}
M.~Selvi, K.~Thangaramya, M.~S. Saranya, K.~Kulothungan, S.~Ganapathy, and
  A.~Kannan.
\newblock Classification of {Medical} {Dataset} {Along} with {Topic} {Modeling}
  {Using} {LDA}.
\newblock In Vijay Nath and Jyotsna~Kumar Mandal, editors, {\em
  Nanoelectronics, {Circuits} and {Communication} {Systems}}, Lecture {Notes}
  in {Electrical} {Engineering}, pages 1--11, Singapore, 2019. Springer.

\bibitem{vayansky2020review}
Ike Vayansky and Sathish~AP Kumar.
\newblock A review of topic modeling methods.
\newblock {\em Information Systems}, 94:101582, 2020.

\bibitem{abdelrazek2022topic}
Aly Abdelrazek, Yomna Eid, Eman Gawish, Walaa Medhat, and Ahmed Hassan.
\newblock Topic modeling algorithms and applications: A survey.
\newblock {\em Information Systems}, page 102131, 2022.

\bibitem{Comparison_Topic_Modeling_Algorithms}
Ashjan Alotaibi and Najwa Altwaijry.
\newblock A comparison of topic modeling algorithms on visual social media
  networks.
\newblock In {\em 2022 2nd International Conference on Computing and
  Information Technology (ICCIT)}, pages 26--31, 2022.

\bibitem{mimno2011optimizing}
David Mimno, Hanna Wallach, Edmund Talley, Miriam Leenders, and Andrew
  McCallum.
\newblock Optimizing semantic coherence in topic models.
\newblock In {\em Proceedings of the 2011 conference on empirical methods in
  natural language processing}, pages 262--272, 2011.

\bibitem{abdelrazek2022topic}
Aly Abdelrazek, Yomna Eid, Eman Gawish, Walaa Medhat, and Ahmed Hassan.
\newblock Topic modeling algorithms and applications: A survey.
\newblock {\em Information Systems}, page 102131, 2022.

\bibitem{yi2009comparative}
Xing Yi and James Allan.
\newblock A comparative study of utilizing topic models for information
  retrieval.
\newblock In {\em Advances in Information Retrieval: 31th European Conference
  on IR Research, ECIR 2009, Toulouse, France, April 6-9, 2009. Proceedings
  31}, pages 29--41. Springer, 2009.
  
\bibitem{vayansky2020review}
Ike Vayansky and Sathish~AP Kumar.
\newblock A review of topic modeling methods.
\newblock {\em Information Systems}, 94:101582, 2020.

      
\bibitem{aldhyani2022detecting}
Theyazn~HH Aldhyani, Saleh~Nagi Alsubari, Ali~Saleh Alshebami, Hasan Alkahtani,
  and Zeyad~AT Ahmed.
\newblock Detecting and analyzing suicidal ideation on social media using deep
  learning and machine learning models.
\newblock {\em International journal of environmental research and public
  health}, 19(19):12635, 2022.

\bibitem{beck2000weisman}
A~Beck and M~Kovacs.
\newblock weisman a.
\newblock {\em Handbook ofpsychiatric measures: Beck Scale for Suicide
  Ideation. American Psychiatric Association}, 2000.

\bibitem{beck1961inventory}
Aaron~T Beck, Calvin~H Ward, Mock Mendelson, Jeremiah Mock, and John Erbaugh.
\newblock An inventory for measuring depression.
\newblock {\em Archives of general psychiatry}, 4(6):561--571, 1961.

\bibitem{burnap2015machine}
Pete Burnap, Walter Colombo, and Jonathan Scourfield.
\newblock Machine classification and analysis of suicide-related communication
  on twitter.
\newblock In {\em Proceedings of the 26th ACM conference on hypertext \& social
  media}, pages 75--84, 2015.

\bibitem{castillo2020suicide}
Gema Castillo-S{\'a}nchez, Gon{\c{c}}alo Marques, Enrique Dorronzoro, Octavio
  Rivera-Romero, Manuel Franco-Mart{\'\i}n, and Isabel De~la Torre-D{\'\i}ez.
\newblock Suicide risk assessment using machine learning and social networks: a
  scoping review.
\newblock {\em Journal of medical systems}, 44(12):205, 2020.

\bibitem{chancellor2020methods}
Stevie Chancellor and Munmun De~Choudhury.
\newblock Methods in predictive techniques for mental health status on social
  media: a critical review.
\newblock {\em NPJ digital medicine}, 3(1):43, 2020.

\bibitem{chen2018}
Xuetong Chen, Martin~D Sykora, Thomas~W Jackson, and Suzanne Elayan.
\newblock What about mood swings: Identifying depression on twitter with
  temporal measures of emotions.
\newblock In {\em Companion proceedings of the the web conference 2018}, pages
  1653--1660, 2018.

\bibitem{de2013predicting}
Munmun De~Choudhury, Michael Gamon, Scott Counts, and Eric Horvitz.
\newblock Predicting depression via social media.
\newblock In {\em Proceedings of the international AAAI conference on web and
  social media}, volume~7, pages 128--137, 2013.

\bibitem{gaur2019knowledge}
Manas Gaur, Amanuel Alambo, Joy~Prakash Sain, Ugur Kursuncu, Krishnaprasad
  Thirunarayan, Ramakanth Kavuluru, Amit Sheth, Randy Welton, and Jyotishman
  Pathak.
\newblock Knowledge-aware assessment of severity of suicide risk for early
  intervention.
\newblock In {\em The world wide web conference}, pages 514--525, 2019.

\bibitem{havigerova2019text}
Jana~M Havigerov{\'a}, Ji{\v{r}}{\'\i} Haviger, Dalibor Ku{\v{c}}era, and Petra
  Hoffmannov{\'a}.
\newblock Text-based detection of the risk of depression.
\newblock {\em Frontiers in psychology}, 10:513, 2019.

\bibitem{hawton2013risk}
Keith Hawton, Carolina~Casa{\~n}as i~Comabella, Camilla Haw, and Kate Saunders.
\newblock Risk factors for suicide in individuals with depression: a systematic
  review.
\newblock {\em Journal of affective disorders}, 147(1-3):17--28, 2013.

\bibitem{he2022deep}
Lang He, Mingyue Niu, Prayag Tiwari, Pekka Marttinen, Rui Su, Jiewei Jiang,
  Chenguang Guo, Hongyu Wang, Songtao Ding, Zhongmin Wang, et~al.
\newblock Deep learning for depression recognition with audiovisual cues: A
  review.
\newblock {\em Information Fusion}, 80:56--86, 2022.

\bibitem{joiner1997modified}
Thomas~E Joiner~Jr, M~David Rudd, and M~Hasan Rajab.
\newblock The modified scale for suicidal ideation: Factors of suicidality and
  their relation to clinical and diagnostic variables.
\newblock {\em Journal of abnormal psychology}, 106(2):260, 1997.

\bibitem{kliem2017german}
S{\"o}ren Kliem, Anna Lohmann, Thomas M{\"o}{\ss}le, and Elmar Br{\"a}hler.
\newblock German beck scale for suicide ideation (bss): psychometric properties
  from a representative population survey.
\newblock {\em BMC psychiatry}, 17(1):1--8, 2017.

\bibitem{kroenke2001phq}
Kurt Kroenke, Robert~L Spitzer, and Janet~BW Williams.
\newblock The phq-9: validity of a brief depression severity measure.
\newblock {\em Journal of general internal medicine}, 16(9):606--613, 2001.

\bibitem{li2022association}
Kuiliang Li, Xiaoqing Zhan, Lei Ren, Nan Liu, Lei Zhang, Ling Li, Ting Chen,
  Zhengzhi Feng, and Xi~Luo.
\newblock The association of abuse and depression with suicidal ideation in
  chinese adolescents: a network analysis.
\newblock {\em Frontiers in psychiatry}, 13, 2022.

\bibitem{lopez2022exploring}
Yolanda L{\'o}pez-Del-Hoyo and Pedro Cerbuna.
\newblock Exploring the risk of suicide in real time on spanish twitter:
  Observational study.
\newblock {\em JMIR Public Health and Surveillance}, 8(5), 2022.

\bibitem{macavaney2021community}
Sean MacAvaney, Anjali Mittu, Glen Coppersmith, Jeff Leintz, and Philip Resnik.
\newblock Community-level research on suicidality prediction in a secure
  environment: Overview of the clpsych 2021 shared task.
\newblock In {\em Proceedings of the Seventh Workshop on Computational
  Linguistics and Clinical Psychology: Improving Access}, pages 70--80, 2021.

\bibitem{malhotra2022deep}
Anshu Malhotra and Rajni Jindal.
\newblock Deep learning techniques for suicide and depression detection from
  online social media: A scoping review.
\newblock {\em Applied Soft Computing}, page 109713, 2022.

\bibitem{mann2020see}
Paulo Mann, Aline Paes, and Elton~H Matsushima.
\newblock See and read: detecting depression symptoms in higher education
  students using multimodal social media data.
\newblock In {\em Proceedings of the International AAAI Conference on Web and
  social media}, volume~14, pages 440--451, 2020.

\bibitem{martinengo2019suicide}
Laura Martinengo, Louise Van~Galen, Elaine Lum, Martin Kowalski, Mythily
  Subramaniam, and Josip Car.
\newblock Suicide prevention and depression apps’ suicide risk assessment and
  management: a systematic assessment of adherence to clinical guidelines.
\newblock {\em BMC medicine}, 17(1):1--12, 2019.

\bibitem{mcgirr2007examination}
Alexander McGirr, Johanne Renaud, Monique Seguin, Martin Alda, Chawki
  Benkelfat, Alain Lesage, and Gustavo Turecki.
\newblock An examination of dsm-iv depressive symptoms and risk for suicide
  completion in major depressive disorder: a psychological autopsy study.
\newblock {\em Journal of affective disorders}, 97(1-3):203--209, 2007.

\bibitem{park2013perception}
Minsu Park, David McDonald, and Meeyoung Cha.
\newblock Perception differences between the depressed and non-depressed users
  in twitter.
\newblock In {\em Proceedings of the international AAAI conference on web and
  social media}, volume~7, pages 476--485, 2013.

\bibitem{pennebaker2001linguistic}
James~W Pennebaker, Martha~E Francis, and Roger~J Booth.
\newblock Linguistic inquiry and word count: Liwc 2001.
\newblock {\em Mahway: Lawrence Erlbaum Associates}, 71(2001):2001, 2001.

\bibitem{posner2011columbia}
Kelly Posner, Gregory~K Brown, Barbara Stanley, David~A Brent, Kseniya~V
  Yershova, Maria~A Oquendo, Glenn~W Currier, Glenn~A Melvin, Laurence
  Greenhill, Sa~Shen, et~al.
\newblock The columbia--suicide severity rating scale: initial validity and
  internal consistency findings from three multisite studies with adolescents
  and adults.
\newblock {\em American journal of psychiatry}, 168(12):1266--1277, 2011.

\bibitem{radloff1977ces}
Lenore~Sawyer Radloff.
\newblock The ces-d scale: A self-report depression scale for research in the
  general population.
\newblock {\em Applied psychological measurement}, 1(3):385--401, 1977.

\bibitem{rissola2020dataset}
Esteban~A R{\'\i}ssola, Seyed~Ali Bahrainian, and Fabio Crestani.
\newblock A dataset for research on depression in social media.
\newblock In {\em Proceedings of the 28th ACM conference on user modeling,
  adaptation and personalization}, pages 338--342, 2020.

\bibitem{shen2017depression}
Guangyao Shen, Jia Jia, Liqiang Nie, Fuli Feng, Cunjun Zhang, Tianrui Hu,
  Tat-Seng Chua, Wenwu Zhu, et~al.
\newblock Depression detection via harvesting social media: A multimodal
  dictionary learning solution.
\newblock In {\em IJCAI}, pages 3838--3844, 2017.

\bibitem{shen2020detecting}
Yanmei Shen, Wenyu Zhang, Bella Siu~Man Chan, Yaru Zhang, Fanchao Meng,
  Elizabeth~A Kennon, Hanjing~Emily Wu, Xuerong Luo, and Xiangyang Zhang.
\newblock Detecting risk of suicide attempts among chinese medical college
  students using a machine learning algorithm.
\newblock {\em Journal of affective disorders}, 273:18--23, 2020.

\bibitem{shetty2020predicting}
Nisha~P Shetty, Balachandra Muniyal, Arshia Anand, Sushant Kumar, and Sushant
  Prabhu.
\newblock Predicting depression using deep learning and ensemble algorithms on
  raw twitter data.
\newblock {\em International Journal of Electrical and Computer Engineering},
  10(4):3751, 2020.

\bibitem{shing2018expert}
Han-Chin Shing, Suraj Nair, Ayah Zirikly, Meir Friedenberg, Hal Daum{\'e}~III,
  and Philip Resnik.
\newblock Expert, crowdsourced, and machine assessment of suicide risk via
  online postings.
\newblock In {\em Proceedings of the fifth workshop on computational
  linguistics and clinical psychology: from keyboard to clinic}, pages 25--36,
  2018.

\bibitem{singh2022startling}
Om~P Singh.
\newblock Startling suicide statistics in india: Time for urgent action, 2022.

\bibitem{tadesse2019detection}
Michael~M Tadesse, Hongfei Lin, Bo~Xu, and Liang Yang.
\newblock Detection of depression-related posts in reddit social media forum.
\newblock {\em IEEE Access}, 7:44883--44893, 2019.

\bibitem{tolentino2018dsm}
Julio~C Tolentino and Sergio~L Schmidt.
\newblock Dsm-5 criteria and depression severity: implications for clinical
  practice.
\newblock {\em Frontiers in psychiatry}, 9:450, 2018.

\bibitem{vuorilehto2014method}
M~Vuorilehto, HM~Valtonen, T~Melartin, P~Sokero, K~Suominen, and
  ET~Isomets{\"a}.
\newblock Method of assessment determines prevalence of suicidal ideation among
  patients with depression.
\newblock {\em European Psychiatry}, 29(6):338--344, 2014.

\bibitem{vuorilehto2006suicidal}
MS~Vuorilehto, Tarja~K Melartin, and ET~Isomets{\"a}.
\newblock Suicidal behaviour among primary-care patients with depressive
  disorders.
\newblock {\em Psychological Medicine}, 36(2):203--210, 2006.

\bibitem{wang2020depression}
Xiaofeng Wang, Shuai Chen, Tao Li, Wanting Li, Yejie Zhou, Jie Zheng, Qingcai
  Chen, Jun Yan, Buzhou Tang, et~al.
\newblock Depression risk prediction for chinese microblogs via deep-learning
  methods: content analysis.
\newblock {\em JMIR medical informatics}, 8(7):e17958, 2020.

\bibitem{whooley2014diagnostic}
Owen Whooley.
\newblock Diagnostic and statistical manual of mental disorders (dsm).
\newblock {\em The Wiley Blackwell Encyclopedia of Health, Illness, Behavior,
  and Society}, pages 381--384, 2014.

\bibitem{eke2010hamilton}
Janet~BW Williams.
\newblock A structured interview guide for the hamilton depression rating
  scale.
\newblock {\em Archives of general psychiatry}, 45(8):742--747, 1988.

\bibitem{xu2016contribution}
Ying Xu, Juan Qi, Yi~Yang, and Xiaozhong Wen.
\newblock The contribution of lifestyle factors to depressive symptoms: A
  cross-sectional study in chinese college students.
\newblock {\em Psychiatry research}, 245:243--249, 2016.

\bibitem{ye2021multi}
Jiayu Ye, Yanhong Yu, Qingxiang Wang, Wentao Li, Hu~Liang, Yunshao Zheng, and
  Gang Fu.
\newblock Multi-modal depression detection based on emotional audio and
  evaluation text.
\newblock {\em Journal of Affective Disorders}, 295:904--913, 2021.

\bibitem{zhang2022natural}
Tianlin Zhang, Annika~M Schoene, Shaoxiong Ji, and Sophia Ananiadou.
\newblock Natural language processing applied to mental illness detection: a
  narrative review.
\newblock {\em NPJ digital medicine}, 5(1):46, 2022.

\bibitem{zheng2020development}
Le~Zheng, Oliver Wang, Shiying Hao, Chengyin Ye, Modi Liu, Minjie Xia, Alex~N
  Sabo, Liliana Markovic, Frank Stearns, Laura Kanov, et~al.
\newblock Development of an early-warning system for high-risk patients for
  suicide attempt using deep learning and electronic health records.
\newblock {\em Translational psychiatry}, 10(1):72, 2020.

\bibitem{zogan2021depressionnet}
Hamad Zogan, Imran Razzak, Shoaib Jameel, and Guandong Xu.
\newblock Depressionnet: learning multi-modalities with user post summarization
  for depression detection on social media.
\newblock In {\em proceedings of the 44th international ACM SIGIR conference on
  research and development in information retrieval}, pages 133--142, 2021.

\bibitem{henry2005short}
Julie~D Henry and John~R Crawford.
\newblock The short-form version of the Depression Anxiety Stress Scales (DASS-21): Construct validity and normative data in a large non-clinical sample.
\newblock {\em British journal of clinical psychology}, 44(2):227--239, 2005.



\end{thebibliography}
